Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-24 analysis/normalized.Rmd
Combination of normalized expressions

```{r}
poly %>%
  count(common_minimized,  sort = TRUE) %>%
  mutate(common_minimized = map_chr(common_minimized, show_set)) %>% 
  mutate(percent = round(100 * n / nb_call_sites, 2)) %>% 
  datatable()
```

>>>>

```{r}
combination_ranking <- poly %>%
  count(common_minimized,  sort = TRUE) %>%
  mutate(common_minimized = map_chr(common_minimized, show_set)) %>% 
  mutate(percent = round(100 * n / nb_call_sites, 2)) %>%
  mutate(cumpercent =cumsum(percent))

combination_ranking %>% 
  datatable()
```

And represented as a bar plot:

```{r}
combination_ranking %>%
  filter(cumpercent < 95) %>%
  ggplot(aes(x = fct_reorder(common_minimized, n), y = percent)) + 
  geom_col() + 
  labs(x = "Combinations", y = "%") +
  coord_flip()
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))

ggsave_prefix("combination_minimized.pdf")
```

### 2021-03-24 paper/main.tex
Combination of normalized expressions

\paragraph{Large expressions }  Compositions of functions, without variables (\c{F(F(X))} minimized expression) is the second most frequent minimized expression. \c{\{BLOCK\}} is a sequence of statements. It is usually large, with in average \packageMinimizedoperationsjRnd operations in it.

@@

The most common combinations for sites with several minimized expressions are:

>>>>

\paragraph{Large expressions.}  Compositions of functions, without variables (\c{F(F(X))} minimized expression) is the second most frequent minimized expression. \c{\{BLOCK\}} is a sequence of statements. It is usually large, with in average \packageMinimizedoperationsjRnd operations in it.

@@

The most common combinations for sites with several minimized expressions are shown in Figure~\ref{fig:frequentcombinationminimized}.

\begin{figure}
	\centering 
	\includegraphics[width=\textwidth]{package_combination_minimized.pdf}
	\caption{Most frequent combinations of minimized expressions per site, with a cumulative share of 95\% of the sites.} \label{fig:frequentcombinationminimized}
\end{figure}
